\tool: Revisiting BadUSB with Type-C

### 2021-01-30 WOOT/Files/experiment.tex
Figures

\begin{figure}[t]
	\includegraphics[width=.98\linewidth]{./Figs/armory_all.png}\\
	\begin{tabular}{ll}
	\mycircled{A}Victim's Device    &\mycircled{B}\tool\\
	\mycircled{1}USB 3.x Hub        &\mycircled{2}Raspberry Pi 4B\\
	\mycircled{3}Auxiliary Power Bank &\mycircled{4}Video Capture\\
	\mycircled{5}ATMEGAA32U4 Board
	\end{tabular}

>>>>

\begin{figure}[t]
	\includegraphics[width=.98\linewidth]{./Figs/armory_all.png}\\
	\begin{tabular}{ll}
	\circled[text=white,fill=myyellow]{\scriptsize{A}} Victim's Device    &\circled[text=white,fill=myyellow]{\scriptsize{B}}~\tool\\
	\circled[text=white,fill=myyellow]{\footnotesize{1}} USB 3.x Hub        &\circled[text=white,fill=myyellow]{\footnotesize{2}} Raspberry Pi 4B\\
	\circled[text=white,fill=myyellow]{\footnotesize{3}} Auxiliary Power Bank &\circled[text=white,fill=myyellow]{\footnotesize{4}} Video Capture\\
	\circled[text=white,fill=myyellow]{\footnotesize{5}} ATMEGAA32U4 Board
	\end{tabular}
